---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# npiShiny

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/parmsam/npiShiny?branch=main&svg=true)](https://ci.appveyor.com/project/parmsam/npiShiny)
<!-- badges: end -->

The goal of npiShiny is to provide a Shiny app for enhanced search of the U.S. National Provider Identifier (NPI) Registry. The original registry is available [here](https://npiregistry.cms.hhs.gov/). This Shiny app leverages the [npi](https://github.com/frankfarach/npi) package which helps access the API (v2.1) from the Center for Medicare and Medicaid Services.

## Try it out
App deployed to shinyapps.io here: https://parmsam.shinyapps.io/npiShiny/

## Installation

<!-- You can install the released version of npiShiny from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("npiShiny") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("parmsam/npiShiny")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# library(npiShiny)
```

## Code of Conduct

Please note that the npiShiny project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

